\Title

### 2023-07-04 Grimaldi-etal-BiolCybernetics.tex
abstract

The precise timing of spikes from afferent neurons determines the response of a biological neuron. This temporal aspect of the neural activity is essential for understanding information processing in neurobiology, and is particularly applicable to the output of neuromorphic hardware such as event-based cameras. Yet, most artificial neural models ignore this important temporal dimension of the neural activity. Here, we develop a model for efficient detection of temporal spiking motifs based on a layer of spiking neurons with heterogeneous synaptic delays. The model exploits the property that the diversity of synaptic delays on the dendritic tree allows for the synchronization of specific arrangements of temporally precise synaptic inputs as they reach the basal dendritic tree. We show that this process can be formalized as a time-invariant logistic regression that can be trained on labeled data. We demonstrate its application to naturalistic videos transformed into event streams similar to the output of the biological retina or event-based cameras. To characterize the robustness of the model in detecting visual motion, we test its efficiency by pruning some weights and show that it is still efficient at very low workloads. In conclusion, heterogeneous delays provide an end-to-end, event-driven computational building block that could improve the performance of future spiking neural network (SNN) algorithms and especially their applications in neuromorphic chips.

@@

>>>>

The precise timing of spikes from afferent neurons determines the response of a biological neuron. This temporal aspect of neural activity is essential for understanding information processing in neurobiology, and is particularly applicable to the output of neuromorphic hardware such as event-based cameras. However, most artificial neural models ignore this important temporal dimension of neural activity. Here, we develop a model for efficiently detecting temporal spiking motifs based on a layer of spiking neurons with heterogeneous synaptic delays. The model exploits the property that the diversity of synaptic delays on the dendritic tree allows specific arrangements of temporally precise synaptic inputs to synchronize as they reach the basal dendritic tree. We show that this process can be formalized as a time-invariant logistic regression that can be trained on labeled data. We demonstrate its application to naturalistic videos transformed into event streams, similar to the output of the biological retina or event-based cameras. To characterize the robustness of the model in detecting visual motion, we test its efficiency by pruning some weights and show that it is still efficient at very low workloads. In conclusion, heterogeneous delays provide an end-to-end, event-driven computational building block that could improve the performance of future spiking neural network (SNN) algorithms and, in particular, their applications in neuromorphic chips.

@@

% TODO citer Levy2021 "Communication consumes 35 times more energy than computation in the human cortex" 
